\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[top=1.25in, bottom=1.25in, left=1.25in, right=1.25in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{center}

\vspace*{1.5em}

{\LARGE\bfseries The 2048 Chrysopoeia:\\[0.4em]
An Explicit Construction Program for the $d=2048$ SIC-POVM Moduli}

\vspace{1.5em}

{\large C.\ Lando Mills}

\vspace{0.6em}

{\normalsize Independent Researcher}

\vspace{0.4em}

{\normalsize Correspondence: \href{mailto:c.landonmills@gmail.com}{c.landonmills@gmail.com}}

\vspace{0.2em}

{\normalsize ORCID: \href{https://orcid.org/0000-0003-0003-0552}{0000-0003-0003-0552}}

\end{center}

\vspace{1.5em}

\noindent\textbf{Declarations}

\vspace{0.8em}

\noindent\textbf{Availability of data and material}

\noindent
The companion formalization and its Lean modules live in the \texttt{p4ramill} library of
\texttt{p4rakernel} (\url{https://github.com/umpolungfish/p4rakernel}), frozen at commit
\texttt{eea2c0c} on branch \texttt{crystalline/manuscripts3-2026-07-07}
(tag \texttt{crystalline-manuscripts3-v1}).
Field computations reported in the manuscript were performed in PARI/GP.
This manuscript trio is frozen in \texttt{ig-docs}
(\url{https://github.com/umpolungfish/ig-docs}) on the same branch name and tag.

\vspace{1em}

\noindent\textbf{Competing interests}

\noindent
The author declares no competing interests.

\vspace{1em}

\noindent\textbf{Funding}

\noindent
This research received no external funding.

\vspace{1em}

\noindent\textbf{Authors' contributions}

\noindent
C.\ Lando Mills: conceptualization, formalization, investigation, validation,
writing (original draft), writing (review and editing).

\vspace{1em}

\noindent\textbf{Acknowledgements}

\noindent
The author thanks Harry T.\ Larson for imparting the importance of catching rising
problems and never letting them go.
The $d=2048$ moduli program was undertaken in the same spirit: when unconstrained
recovery stalled at a spurious local minimum, the route through Stark units, the ray
class tower, and the integer norm sieve was not dropped.
Field computations were performed in PARI/GP; the companion formalization is the
SIC--Stark--12th manuscript in this trio.

\end{document}