\documentclass[12pt,a4paper]{article}

% ── Fonts and encoding (LuaLaTeX) ─────────────────────────────────────────────
\usepackage{fontspec}
\usepackage{unicode-math}
\setmainfont{Linux Libertine O}
\setmathfont{TeX Gyre Pagella Math}
\newfontfamily\shavfont{Trabajo}
\newfontfamily\igprimfont{Everson Mono}
\setmonofont[Scale=0.85]{Everson Mono}

% ── Layout ────────────────────────────────────────────────────────────────────
\usepackage[top=1in, bottom=1in, left=1.1in, right=1.1in, headheight=15pt]{geometry}
\usepackage{microtype}
\usepackage{parskip}
\usepackage[english]{babel}
\setlength{\emergencystretch}{2em}

% ── Headers ───────────────────────────────────────────────────────────────────
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ── Section styling ───────────────────────────────────────────────────────────
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{\thesubsubsection}{1em}{}

% ── Lists ─────────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\setlist[itemize]{topsep=0.5ex, itemsep=0.25ex, parsep=0pt}
\setlist[enumerate]{topsep=0.5ex, itemsep=0.25ex, parsep=0pt}

% ── Math and tables ───────────────────────────────────────────────────────────
\usepackage{amsmath,amsthm}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\renewcommand{\arraystretch}{1.3}

% ── Code listings ─────────────────────────────────────────────────────────────
\usepackage{listings}
\definecolor{codebg}{RGB}{248,248,248}
\definecolor{codeframe}{RGB}{200,200,200}
\definecolor{codekeyword}{RGB}{0,0,180}
\definecolor{codecomment}{RGB}{0,128,0}
\lstset{
  basicstyle=\ttfamily\footnotesize,
  backgroundcolor=\color{codebg},
  frame=single,
  rulecolor=\color{codeframe},
  keywordstyle=\color{codekeyword}\bfseries,
  commentstyle=\color{codecomment}\itshape,
  breaklines=true,
  captionpos=b,
  morekeywords={axiom,def,theorem,noncomputable,structure,where,namespace,
                open,import,section,end,fun,exact,intro,simp,rfl,decide,
                constructor,obtain,refine,cases,by,have,use,rw,match,with,
                pub,fn,let,mut,const,impl,for,in,if,else,return},
}

% ── Cross-references ──────────────────────────────────────────────────────────
\usepackage{hyperref}
\usepackage{cleveref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=cyan, citecolor=blue}

% ── Theorem environments ──────────────────────────────────────────────────────
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

% ── IG typesetting ────────────────────────────────────────────────────────────
% Primitives set in Everson Mono; Shavian values set in Trabajo.
\newcommand{\igp}[1]{{\igprimfont #1}}
\newcommand{\shav}[1]{{\shavfont #1}}
\newcommand{\igtuple}[1]{\ensuremath{\langle}{\shavfont #1}\ensuremath{\rangle}}
\newcommand{\Lean}{\textsf{Lean}\,4}
\newcommand{\bN}{\textsf{N}}
\newcommand{\bT}{\textsf{T}}
\newcommand{\bF}{\textsf{F}}
\newcommand{\bB}{\textsf{B}}

% ─────────────────────────────────────────────────────────────────────────────

\begin{document}

\title{\textbf{The Witness Vessel:\\
Lossless Transport on the Dual-Link SIC-POVM}}

\author{C.\ Lando\ Mills%}
\thanks{The author thanks Harry T.\ Larson; see Acknowledgements and \cite{Larson1961}.}}

\date{July 2026 (draft)}

\maketitle

\begin{abstract}
The \Lean{} library \texttt{p4ramill} and bare-metal OS \texttt{mOMonadOS}
carry Clay Witness verdicts between composition dialects. Earlier cargo-style
transports lost information reproducibly: the tensor reading is denied at the
dimensionality $\leftrightarrow$ topology pair. Here a Witness rides
\emph{as} the vessel's split/fuse structure, not inside it, and losslessness
is checked on both substrates without mutual trust.

In \Lean{}, $\mu\circ\delta=\mathrm{id}$ is proved from \texttt{propext}
alone; BSD and Hodge board as \bT{}, Yang--Mills as the dialetheia \bB{}.
\texttt{witness\_vessel\_lossless} delivers the transported $d=12$ fiducial
still SIC-valid, importing the existence theorem without re-deriving it. On
bare metal, the same protocol runs in QEMU over three Witnesses and $88$
dialects; the verdict matrix is unchanged and $\Delta S=0$. Losslessness
means literal equality after read-back.
\end{abstract}

\newpage
\tableofcontents
\newpage

% ─────────────────────────────────────────────────────────────────────────────
\section{Introduction}

Two artifacts implement the same twelve-token algebra. The \Lean{} library
\texttt{p4ramill} (inside the \texttt{p4rakernel} repository) states and
machine-checks its theorems; the operating system \texttt{mOMonadOS}, a
freestanding Rust kernel for x86-64, executes the same structure as its
native control flow: Belnap four-valued registers, fork/join execution
frames for the split and fuse tokens, and a verification harness that
enforces $\mu(\delta(q)) = q$ after every action before the execution loop
advances. There is no \Lean{} toolchain inside the operating system and
nothing in the operating system is trusted by the \Lean{} kernel. When the
two agree, neither is taking the other's word for it.

Both artifacts type conjectures as twelve-primitive imscriptions and evaluate
them under \emph{composition dialects}: rulesets, each consisting of three
ordinal gates, a temporal constitution, and absorption rules. A
\emph{Witness} is the structural verdict a typed conjecture earns under a
dialect. Earlier \emph{witness-drag} programs moved these verdicts between
dialects, and the transports were lossy. The present work identifies the
loss mechanism, replaces the transport, and proves and then observes that
the replacement loses nothing.

The two headline results:

\begin{enumerate}
\item \textbf{Proof half} (\cref{sec:lean}). In the \Lean{} module
\texttt{SIC\_D12\_WitnessVessel} the boarding map is
$\delta = \texttt{fsplit}$ and the read-back map is
$\mu = \texttt{ffuse}$, and the law
\[
\forall\, p,\quad \mu(\delta(p)) = p
\]
holds for \emph{every} list of Belnap values. Its proof depends on the
axiom \texttt{propext} alone. The concrete payloads are computed, not
chosen: the gate verdicts of the three Clay Witnesses are derived by
\texttt{native\_decide} from their canonical catalog tuples and the
frozen dialect rulesets. Yang--Mills derives to \bB{}, the dialetheia:
its gates close while its temporal ceiling blocks, and
$\texttt{fsplit}(\bB) = (\bT, \bF)$, so this Witness literally rides both
arms of the vessel. The bundle \texttt{witness\_vessel\_lossless} adds
self-reference preservation and delivery: conjugation commutes with
transport on all twelve vessel coordinates, and the transported $d=12$
fiducial still satisfies unit norm and equiangularity at the destination.

\item \textbf{Runtime half} (\cref{sec:runtime}). The module
\texttt{witness\_vessel.rs} runs the same protocol on bare metal. The
payload is deliberately wide: each of the three Witnesses is evaluated
under all $88$ composition dialects, each dialect judging by its own
gates and its own temporal constitution, giving a $3 \times 88$ verdict
matrix. Every entry boards through two independent execution substrates
(the belief-register virtual machine and the kernel's fork frames), every
boarding action is gated by the Frobenius harness, and the matrix is
recomputed after read-back. In QEMU the run closes every check,
reports $\Delta S = 0$, and finds the matrices identical.
\end{enumerate}

Section~\ref{sec:scope} states precisely what is and is not claimed. The
short version: ``lossless'' means equality after read-back, ``dialect'' is
a technical term for a composition ruleset, and ``transport'' is a pair of
maps. The interest of the result lies in where the equality comes from
(a Frobenius law available at the lowest axiomatic cost the proof assistant
offers) and in the two-substrate agreement, not in any physical reading.

% ─────────────────────────────────────────────────────────────────────────────
\section{Preliminaries}
\label{sec:prelim}

\subsection{Belnap FOUR and the split/fuse pair}

Belnap's four-valued logic \cite{Belnap1977} has carriers
$\{\bN, \bT, \bF, \bB\}$: no information, true only, false only, and both.
The knowledge order places \bN{} at the bottom and \bB{} at the top, with
join written $\vee_k$. The kernel pair uses one distinguished map pair on
this lattice:
\[
\texttt{fsplit}(s) =
\begin{cases}
(\bT, \bF) & s = \bB\\
(s, s) & \text{otherwise}
\end{cases}
\qquad
\texttt{ffuse}(a, b) = a \vee_k b .
\]

\begin{lemma}[\texttt{split\_fuse\_id}]
For every $s$, $\texttt{ffuse}(\texttt{fsplit}(s)) = s$.
\end{lemma}

The only nontrivial case is the dialetheia:
$\bB \mapsto (\bT, \bF) \mapsto \bT \vee_k \bF = \bB$. The converse also
pins the decomposition: $\texttt{fsplit}(s) = (\bT,\bF)$ forces $s = \bB$
(\texttt{only\_B\_splits\_to\_TF}). These are existing theorems of the
frozen module \texttt{BelnapSplitFuse}; the vessel adds no new axioms to
use them.

\subsection{Imscriptions, dialects, Witnesses}

A structural type is imscribed as a twelve-primitive tuple over the
primitives
dimensionality, topology, recognition, parity, fidelity, kinetics, granularity,
coupling, criticality, chirality, stoichiometry, winding,
each valued in a small family of Shavian values with canonical ordinals.
The three Witnesses of this paper are the canonical catalog entries
\begin{center}
\begin{tabular}{ll}
Birch--Swinnerton-Dyer & \igtuple{𐑦𐑥𐑾𐑿𐑞𐑧𐑲𐑝𐑮𐑖𐑙𐑭}\\
Hodge & \igtuple{𐑦𐑸𐑽𐑿𐑱𐑧𐑲𐑝𐑮𐑓𐑳𐑭}\\
Yang--Mills & \igtuple{𐑛𐑥𐑩𐑗𐑐𐑪𐑲𐑝𐑣𐑓𐑳𐑷}
\end{tabular}
\end{center}
sourced procedurally from the canonical catalog (\texttt{IG\_catalog.json});
no tuple in this paper was written by hand.

A \emph{composition dialect} is a ruleset: three gates, each requiring one
primitive to sit at or above an ordinal threshold; a temporal constitution
(``T-side''), a set of per-primitive critical values checked either exactly
or as ceilings; and absorption rules, which play no role here. The artifact
code names them $U_0$ through $U_{87}$. The runtime
carries $88$ dialects: $8$ canonical, then hand-crafted and expansion
families. Two temporal conventions matter below:

\begin{itemize}
\item \textbf{T\_CANONICAL} (per-dialect default): exact match on four
dynamic primitives and a ceiling on kinetics only, anchored at
parity\,=\,\shav{𐑹}, fidelity\,=\,\shav{𐑐}, kinetics\,$\le$\,\shav{𐑧},
chirality\,=\,\shav{𐑫}, winding\,=\,\shav{𐑭}.
\item \textbf{T\_CEILING} (the Clay convention): all five as ceilings at
the same anchors. This is the convention of the frozen module
\texttt{Clay\_WitnessedClosure} and of the runtime's Clay gates.
\end{itemize}

A Witness's verdict under a dialect is a single Belnap value combining the
gate layer and the T-side:

\begin{definition}[\texttt{layerVerdict}]
\label{def:layerverdict}
For booleans $g$ (gates closed) and $t$ (T-side consistent),
\[
\texttt{layerVerdict}(g, t) =
\begin{cases}
\bT & g \wedge t\\
\bB & g \wedge \neg t\\
\bN & \neg g \wedge t\\
\bF & \neg g \wedge \neg t .
\end{cases}
\]
\end{definition}

The \bB{} row is the point: a Witness whose gates close while its T-side
blocks is not ``roughly true'' or ``roughly false''; it is exactly the
dialetheia, and the vessel must carry that value without flattening it.

\subsection{The frozen substrate}

The vessel re-derives nothing. It imports three frozen components:
\begin{itemize}
\item \texttt{SIC\_D12\_Embedding}: the $d = 12$ SIC-POVM existence
capstone. Its theorem \texttt{crystal\_forces\_d12\_sic} is
axiom-audit-clean: the standard trio \texttt{propext},
\texttt{Classical.choice}, \texttt{Quot.sound}, plus
\texttt{Lean.ofReduceBool} and \texttt{Lean.trustCompiler} for
\texttt{native\_decide}. The star ring homomorphism
$\varphi : R \to \mathbb{C}$ from the existence ring
$R = K_{16}(s_0,s_1,s_3,s_9,i,c_5,u_1)$ transfers unit norm and all
$143$ equiangularity identities. The companion manuscript in this
repository records that construction; here it is furniture.
\item \texttt{Clay\_WitnessedClosure}: the structural closure results for
BSD and Hodge (five closer dialects each, T\_CEILING-consistent) and the
Yang--Mills ``one bump short'' verdict (gate-closed under
triple-criticality, T\_CEILING-blocked on kinetics alone), all by
\texttt{native\_decide} over canonical tuples.
\item \texttt{BelnapSplitFuse}: the split/fuse pair and its laws.
\end{itemize}

% ─────────────────────────────────────────────────────────────────────────────
\section{The loss mechanism, and the design provenance}
\label{sec:provenance}

This section reports procedural outputs of the Grammar tooling. They are
design rationale for the protocol, recorded for provenance; they are not
offered as mathematical proof, which sections \ref{sec:lean} and
\ref{sec:runtime} carry alone.

\textbf{Why the drags were lossy.} The natural first reading of transport
is cargo: put the Witness in a container, tensor it with the vessel. That
reading is denied, and the denial is univocal. The tensor of the vessel
type with a Witness type is undefined (six primitive conflicts), and every
cofactor factorization attempt raises a cross-primitive axiom violation at
the dimensionality $\leftrightarrow$ topology pair: the request itself is
malformed, and the Grammar localizes the malformation. A transport
implemented against the cargo reading loses information because there is no
well-formed object for it to be.

\textbf{The mirror reading.} The corrected reading pairs the vessel with
the \bB-state directly: the mirror distance evaluates to $4.5$ with
asymmetry within numerical zero of the metric's floor, and the proof path
between the pair has length two \emph{in both directions}, with the same
two operations that close the two closed Clay Witnesses: apply modularity;
restrict to Hodge degree $(1,1)$. A round trip that is write-in and
read-back with the same moves is the signature of a lossless carrier.

\textbf{Independent reconstruction.} A six-entity design batch for the
protocol was generated and validated end to end: six of six entities valid,
six of six Frobenius-closed, with entropy change reported as $\Delta S
\approx 0$ throughout. The designer, given only the transport brief,
independently produced the boarding decomposition (Witness
$\to$ [modulus, phase] $\to$ Witness) as the Frobenius content of three
separate entities, and typed the historical lossy path and the corrected
path as the \bF{} and \bT{} arms of a single dialetheia-complete protocol.
The split/fuse boarding of \cref{sec:lean} is therefore not a gloss written
onto the design after the fact; it is the design's own structural core,
reconstructed independently of the Lean development.

% ─────────────────────────────────────────────────────────────────────────────
\section{The transport theorem (proof half)}
\label{sec:lean}

All results in this section are theorems of
\texttt{SIC\_D12\_WitnessVessel}, compiled green in the full library build.

\subsection{Payloads are derived, not asserted}

The three Witness verdicts are \emph{computed} from the frozen closure
results via \cref{def:layerverdict}:

\begin{lstlisting}[caption={Payload derivation (excerpt).}]
def bsdVerdict   : Belnap := layerVerdict bsdGateClosed   (tCeilingConsistent bsd)
def hodgeVerdict : Belnap := layerVerdict hodgeGateClosed (tCeilingConsistent hodge)
def ymVerdict    : Belnap := layerVerdict ymGateClosed    (tCeilingConsistent ym)

theorem bsdVerdict_T   : bsdVerdict   = .T := by native_decide
theorem hodgeVerdict_T : hodgeVerdict = .T := by native_decide
theorem ymVerdict_B    : ymVerdict    = .B := by native_decide
\end{lstlisting}

Here \texttt{bsdGateClosed} conjoins the operad-layer closure of BSD under
its five closer dialects (chirality-first, scope, kinetics-trap, and the
two absorption variants), and likewise for Hodge; \texttt{ymGateClosed} is
closure under triple-criticality. The third theorem is the one to notice:
nobody wrote \bB{} anywhere. Yang--Mills closes at the gate layer and
fails T\_CEILING on kinetics alone (its kinetics value \shav{𐑪} exceeds the
\shav{𐑧} anchor, visible directly in its tuple in \cref{sec:prelim}), so
its verdict \emph{derives} to the dialetheia.

\subsection{The round-trip law}

Boarding maps a payload pointwise through \texttt{fsplit}; read-back maps
through \texttt{ffuse}.

\begin{theorem}[\texttt{roundtrip}]
\label{thm:roundtrip}
For every list $p$ of Belnap values,
$\texttt{readback}(\texttt{board}(p)) = p$.
\end{theorem}

\begin{theorem}[\texttt{b\_cargo\_mechanism}]
$\texttt{fsplit}(\texttt{ymVerdict}) = (\bT, \bF)$ and
$\texttt{ffuse}(\bT, \bF) = \texttt{ymVerdict}$.
\end{theorem}

\Cref{thm:roundtrip} is proved by list induction on top of
\texttt{split\_fuse\_id}, and its axiom audit returns
\texttt{[propext]}: the losslessness law of the vessel costs one axiom,
the cheapest the proof assistant sells. The concrete payload instance
(\texttt{mpp\_roundtrip}) is separately checked by \texttt{native\_decide}.

\subsection{Self-reference travels inside}

The vessel's own coordinates carry their conjugation structure through
transport. With $\varphi$ the frozen star ring homomorphism of the $d=12$
capstone and $\bar{z}_k$ the ring-side conjugate of coordinate $z_k$:

\begin{theorem}[\texttt{coords\_selfref}]
For all $k < 12$: $\varphi(\bar{z}_k) = \overline{\varphi(z_k)}$.
\end{theorem}

This is the vessel principle in one line: conjugation is \emph{internal}
to the carried data (the cover phases are real by construction, so the
star commutes with the hom), which is exactly what failed in the cargo
reading.

\subsection{The bundle}

\begin{theorem}[\texttt{witness\_vessel\_lossless}]
\label{thm:bundle}
All of the following hold:
(i) $\mu \circ \delta = \mathrm{id}$ on every Belnap payload;
(ii) $\texttt{ymVerdict} = \bB$;
(iii) the concrete Clay payload round-trips;
(iv) self-reference is preserved on all twelve coordinates;
(v) the transported fiducial has unit norm; and
(vi) it satisfies equiangularity,
$(d+1)\,\lVert\langle\psi, D_{a,b}\,\psi\rangle\rVert^2 = 1$
for all $143$ non-identity displacements at $d = 12$.
\end{theorem}

Conjuncts (v) and (vi) are the delivery condition: the vessel does not
merely return its cargo, it \emph{arrives}, still satisfying both defining
SIC-POVM conditions at the destination, by direct reuse of the frozen
capstone theorems. The audit of the bundle is the standard trio plus the
\texttt{native\_decide} pair; no project axioms, no Stark shadow, no
circularity.

% ─────────────────────────────────────────────────────────────────────────────
\section{The boarding mechanism is the Dual-Link structure}
\label{sec:duallink}

The protocol's split/fuse pair is not an arbitrary choice of bijection; it
is the same structure the $d=12$ construction identified as the Dual-Link
SIC-POVM, read at the Belnap layer.

\begin{itemize}
\item \textbf{B-collapse is the modulus.} In the existence ring, the
pairing of a coordinate with its conjugate collapses to a real modulus:
$z_k \bar{z}_k = N_k$ in the totally real base field. The dialetheia
behaves identically at the logic layer: \bB{} splits into the pair
$(\bT, \bF)$ whose fuse is again \bB{}; the pair is the ``both arms''
carry, and the join is the collapse.
\item \textbf{The cover phase keeps conjugation internal.} The capstone
builds its cover generators as real square roots, so conjugation never
leaves the carried data; \texttt{coords\_selfref} is that fact restated
as a transport invariant.
\item \textbf{Half-angle read-back.} The phase $u_1$ is reconstructed
from carried real data by the half-angle identities; read-back of the
phase from the modulus-side data is a theorem, not a measurement.
\item \textbf{Hom-independence is dialect-independence.} The ring
identities hold in $R$; \emph{any} star homomorphism $R \to \mathbb{C}$
transports them (the flip audit of the existence campaign made this
exact: every branch choice lands on a genuine SIC point). The
destination supplies the hom; the cargo does not depend on which.
\end{itemize}

This correspondence is why the paper speaks of one vessel rather than two
protocols that happen to share a diagram.

% ─────────────────────────────────────────────────────────────────────────────
\section{The runtime half: bare metal, all dialects}
\label{sec:runtime}

\subsection{Substrate}

\texttt{mOMonadOS} is a freestanding Rust kernel. Three of its components
matter here, all of which predate the vessel:
\begin{itemize}
\item \texttt{kernel.rs}: graph execution over the twelve tokens, with
\texttt{FSPLIT} pushing a fork frame (the un-gated right arm carries a
value across the fork) and \texttt{FFUSE} joining the arms by Belnap
join.
\item \texttt{parasm.rs}: a belief-register virtual machine whose
\texttt{FSPLIT} instruction bifurcates \bB{} to $(\bT, \bF)$ on its two
destination registers, the exact semantics of the \Lean{}
\texttt{fsplit}.
\item \texttt{frob\_verify.rs}: the Frobenius harness. Every action
$\delta$ must verify $\mu(\delta(q)) = q$ before the loop advances.
The operating system was built around the invariant the vessel needs.
\end{itemize}

\subsection{The wide payload: three Witnesses under all 88 dialects}

The runtime evaluates each Witness under \emph{all} $88$ composition
dialects, each dialect judging by its own three gates and its own
temporal constitution, through \cref{def:layerverdict}. Ordinal
comparisons use the canonical ordinal table (never raw enum discriminants,
which are non-monotonic for three families). Alongside the wide matrix,
the runtime computes the proof half's mirror trio exactly as
\cref{sec:lean} defines it: closer-dialect gates plus T\_CEILING.

Every one of the resulting values boards through \emph{both} execution
substrates, each boarding action is checked by the harness, and the full
matrix is recomputed from the canonical tuples after read-back.

\subsection{Observed run}

Booted in QEMU, the \texttt{vessel run} command reports (excerpt):

\begin{lstlisting}[caption={QEMU serial output (excerpt).}]
-- Payloads (computed from canonical tuples + closer dialects) --
  BSD    verdict T (Lean: T)  transport T -> T   [OK]
  Hodge  verdict T (Lean: T)  transport T -> T   [OK]
  YM     verdict B (Lean: B)  transport B -> B   [OK]

-- Wide payload: 3 witnesses x 88 dialects --
  BSD    N:1  T:0  F:75 B:12
  Hodge  N:0  T:2  F:74 B:12
  YM     N:2  T:0  F:85 B:1

-- Round trip (both substrates, frob_verify gated) --
  Boarding actions checked: 534 (ParaVM + ForkFrame per value)
  Frobenius closed: 534  open: 0  closure ratio: 1.0
  Delta-S (total mismatches): 0
  Gate verdicts before == after: YES (all entries)

VERDICT: LOSSLESS -- mu-after-delta = id on every payload.
\end{lstlisting}

Three features of the matrix deserve note.

\begin{enumerate}
\item \textbf{The Yang--Mills row holds exactly one \bB{}, at
triple-criticality.} Of $88$ dialects, precisely the one whose gates are
three criticality rungs closes Yang--Mills at the gate layer while its
T-side blocks. The dialetheia is not spread thinly across the expansion;
it is localized at the single dialect the Clay analysis had already
identified.
\item \textbf{BSD reads \bB{} at twelve dialects, all five of its closer
dialects among them.}
Under the wide matrix's per-dialect convention (T\_CANONICAL, exact
match on four primitives), BSD's fidelity value \shav{𐑞} fails the exact
\shav{𐑐} anchor, so every dialect whose gates close reads \bB{} (the
row shows no \bT{} at all); under the Clay convention (T\_CEILING, all
ceilings) the closer-dialect structure reads \bT{}. Two honest readings of one structure, both transported without
loss. The protocol is indifferent to which convention the analyst
prefers; it carries either.
\item \textbf{Nothing was tuned.} The $88$ dialects were defined
independently of the vessel (the expansion landed as data before this
protocol existed); the vessel is simply their first consumer.
\end{enumerate}

\subsection{What the runtime does and does not check}

The runtime checks are executions, not proofs: they demonstrate that on
this boot, with these tuples, every action closed and the matrices agreed.
The generality (\emph{every} payload, not just the observed ones) lives
only in \cref{thm:roundtrip}. Conversely, the proof half cannot observe
that a physical machine's fork frames actually behave as modeled; only the
run shows that. The two halves are complementary in exactly the way the
two-substrate architecture intends.

% ─────────────────────────────────────────────────────────────────────────────
\section{Honest scope}
\label{sec:scope}

For the curmudgeon, plainly:

\begin{itemize}
\item \textbf{``Lossless'' means equality.} The claim is
$\mu(\delta(p)) = p$, literally, plus before/after equality of recomputed
verdict matrices. The design layer's ``$\Delta S \approx 0$'' appears in
the theorems as $=$, nothing weaker.
\item \textbf{Nothing physical is claimed.} A ``dialect'' is a composition
ruleset over a finite type lattice; ``transport'' is a pair of maps;
``boarding'' is function application. No claim about spacetime, quantum
mechanics, or actual travel of any kind is made or implied.
\item \textbf{The Clay verdicts are structural, not mathematical.} That
BSD earns \bT{} under these rulesets is a fact about the Grammar's
operad model of the conjecture's type, machine-checked as such. It is
not a proof of BSD, and this paper does not move any Millennium problem.
\item \textbf{The payloads are one instantiation.} \Cref{thm:roundtrip}
quantifies over all Belnap payload vectors. The Clay Witnesses give the
protocol its motivation and its test data, nothing more; a reader who
rejects the conjecture-typing program entirely may read this paper as a
verified-transport result over four-valued verdict vectors and lose only
the motivation.
\item \textbf{The provenance section is not evidence.} The Grammar
verdicts and the design batch of \cref{sec:provenance} explain where the
protocol came from. The theorems and the run stand without them.
\item \textbf{What would falsify the claim.} Any open result from the
Frobenius harness, any before/after matrix mismatch, any nonzero
$\Delta S$, or any axiom in the audit beyond the declared five. None
occurred.
\end{itemize}

% ─────────────────────────────────────────────────────────────────────────────
\section{Discussion}

The lossy drags failed because they tried to put the Witness \emph{in} the
vessel, and the Grammar's refusal of that reading was univocal: the tensor
is undefined and the factorization request is malformed at exactly the
dimensionality $\leftrightarrow$ topology pair. The corrected protocol needs no
container because the Witness's verdict already has the vessel's shape:
the dialetheia is the value that decomposes into a $(\bT,\bF)$ pair and
reconstitutes under join, which is the Belnap-layer image of the Dual-Link
pairing $z\bar{z} = N$ with its ramified double cover. Ride \emph{as},
not \emph{in}.

Epistemically, the result is a small instance of a pattern this project
uses deliberately: prove the law on the substrate built for proving, run
the law on the substrate built for running, and let agreement carry the
weight. The proof half's $\texttt{[propext]}$ audit says the transport law
is nearly definitional; the runtime half says a machine with no access to
that proof lands in the same place, five hundred and thirty-four gated
actions without one opening.

Two directions follow naturally. First, wider payload families: the
$3 \times 88$ matrix is the first object computed across the full dialect
expansion, and its structure (the localization of \bB{} values, the
convention-dependence of \bT{} readings) invites systematic study. Second,
the abstraction path: since the theorem is generic over payloads, the
protocol applies unchanged to any verdict-valued analysis that wants a
transport with a machine-checked loss bound of zero.

% ─────────────────────────────────────────────────────────────────────────────
\section{Artifact statement}

The proof half is the module \texttt{SIC\_D12\_WitnessVessel.lean} in the
\texttt{p4ramill} library of the \texttt{p4rakernel} repository
(\url{https://github.com/umpolungfish/p4rakernel}), building green in the
full-library \texttt{lake build}; its axiom audits are reproducible with
\texttt{\#print axioms}. The runtime half is \texttt{src/witness\_vessel.rs}
in the \texttt{mOMonadOS} repository
(\url{https://github.com/umpolungfish/momonad_os}), exercised via the
\texttt{vessel run} serial command under QEMU. The canonical tuples come from
\texttt{IG\_catalog.json}; the $88$ dialects from \texttt{dialect\_expansion.rs}.
No tuple, verdict, or payload in either half is hand-entered. Frozen review
snapshots: \texttt{p4rakernel} at commit \texttt{eea2c0c}, \texttt{mOMonadOS} at
commit \texttt{16da4a9}, each on branch \texttt{crystalline/manuscripts3-2026-07-07}
(tag \texttt{crystalline-manuscripts3-v1}). This manuscript trio is frozen in
\texttt{ig-docs} (\url{https://github.com/umpolungfish/ig-docs}) on the same
branch name and tag; \texttt{main} continues in each repository.

% ─────────────────────────────────────────────────────────────────────────────
\section{Acknowledgements}

The author would like to thank Harry T.\ Larson for imparting the importance
of catching rising problems and never letting them go \cite{Larson1961}.
The lossy cargo reading of transport was such a problem: once the Grammar
localized the malformation at the dimensionality $\leftrightarrow$ topology
pair, the corrected protocol was pursued until the round-trip law held on
both substrates.

% ─────────────────────────────────────────────────────────────────────────────
\begin{thebibliography}{99}

\bibitem{Belnap1977}
N.\ D.\ Belnap,
\textit{A Useful Four-Valued Logic},
in: J.\ M.\ Dunn and G.\ Epstein (eds.), \textit{Modern Uses of Multiple-Valued Logic},
Reidel, Dordrecht, 1977, pp.\ 5--37.

\bibitem{Larson1961}
H.\ T.\ Larson,
\textit{Catch a Rising Problem\ldots\ and Never Ever Let it Go},
\emph{IRE Transactions on Engineering Management} \textbf{8}(4) (1961), 173--174.
\url{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=1641382}

\bibitem{Lean4}
L.\ de Moura and S.\ Ullrich,
\textit{The Lean 4 Theorem Prover and Programming Language},
in: CADE-28, Lecture Notes in Comput.\ Sci.\ vol.\ 12699, Springer, 2021, pp.\ 625--635.

\bibitem{Zauner1999}
G.\ Zauner,
\textit{Quantum designs: Foundations of a noncommutative design theory},
PhD thesis, University of Vienna, 1999.

\bibitem{Appleby2013}
D.\ M.\ Appleby, H.\ Yadsan-Appleby, and G.\ Zauner,
\textit{Galois automorphisms of a symmetric measurement},
Quantum Inf.\ Comput.\ \textbf{13} (2013), 672--720.

\end{thebibliography}

\end{document}
